### 2021-03-05 introduction.tex
Add a missing reference to sec Training in Introduction
one more typo

Our recommender uses a relational graph convolutional neural network \cite{Schlichtkrull2017}
to represent the problem structure. It learns from the ATP performance on selected problems
and pairs of randomly sampled precedences. This information is used to train
a \emph{symbol cost model}, which then realizes the recommendation by simply sorting 
the problem's symbols according the obtained costs.

@@

The rest of this paper is organized as follows.
\Cref{sec:preliminaries} exposes the basic terminology used throughout the remaining sections.
\Cref{sec:architecture} proposes a structure of the precedence recommender that can be trained on pairs of symbol precedences.
\Cref{sec:evaluation} summarizes and discusses experiments performed
using an implementation of the precedence recommender.
\Cref{sec:related} compares the system proposed in this work with notable related works.
\Cref{sec:conclusion} concludes the investigation and outlines possible directions for future research.

>>>>

Our recommender uses a relational graph convolutional neural network \cite{Schlichtkrull2017}
to represent the problem structure. It learns from the ATP performance on selected problems
and pairs of randomly sampled precedences. This information is used to train
a \emph{symbol cost model}, which then realizes the recommendation by simply sorting 
the problem's symbols according to the obtained costs.

@@

The rest of this paper is organized as follows.
\Cref{sec:preliminaries} exposes the basic terminology used throughout the remaining sections.
\Cref{sec:architecture} proposes a structure of the precedence recommender that can be trained on pairs of symbol precedences,
as described in \cref{sec:training}.
\Cref{sec:evaluation} summarizes and discusses experiments performed
using an implementation of the precedence recommender.
\Cref{sec:related} compares the system proposed in this work with notable related works.
\Cref{sec:conclusion} concludes the investigation and outlines possible directions for future research.
